Grid Test

### 2022-10-17 graphs_newt_snakes/grid_test.Rmd
Looking at how differt grid values, cost values, and map size impast newt and snake coevolution. More wrtiing too come.

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

```
```{r, whale}
min_gen=5000
max_gen=10000
rep=1

whale_gen(GA1_lit_grid_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```
```{r, combo myplots}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(GA1_cor_grid_2_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

boxplot_cors_by_gen(GA1_cor_grid_3_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

boxplot_cors_by_gen(GA1_cor_grid_4_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

boxplot_cors_by_gen(GA1_cor_grid_5_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

boxplot_cors_by_gen(GA1_cor_grid_6_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

boxplot_cors_by_gen(GA1_cor_grid_7_file, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

@@

### Plot 1
```{r, GA1 cor by dif windows}
ginmin = 0
ginmax = 5000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

@@

```{r, GA1 cor by dif windows 2}
ginmin = 5000
ginmax = 10000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 3
```{r, GA1 cor by dif windows 3}
ginmin = 10000
ginmax = 15000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 4
```{r, GA1 cor by dif windows 4}
ginmin = 15000
ginmax = 20000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 5
```{r, GA1 cor by dif windows 5}
ginmin = 20000
ginmax = 25000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 6
```{r, GA1 cor by dif windows 6}
ginmin = 25000
ginmax = 30000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 7
```{r, GA1 cor by dif windows 7}
ginmin = 30000
ginmax = 35000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 8
```{r, GA1 cor by dif windows 8}
ginmin = 35000
ginmax = 40000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 9
```{r, GA1 cor by dif windows 9}
ginmin = 40000
ginmax = 45000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 10
```{r, GA1 cor by dif windows 10}
ginmin = 45000
ginmax = 50000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

>>>>

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, mycolor){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno)), color = mycolor)+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

```{r, whale}
min_gen=5000
max_gen=10000
rep=1

whale_gen(GA1_lit_grid_file, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

```{r, combo myplots}

ginmin = 10000
ginmax = 15000
thecolors=c("#F8766D", "#B79F00", "#00BA38", "#00BFC4", "#619CFF", "#F564E3")

boxplot_cors_by_gen(GA1_cor_grid_2_file, "Grid 2: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[1])

boxplot_cors_by_gen(GA1_cor_grid_3_file, "Grid 3: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[2])

boxplot_cors_by_gen(GA1_cor_grid_4_file, "Grid 4: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[3])

boxplot_cors_by_gen(GA1_cor_grid_5_file, "Grid 5: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[4])

boxplot_cors_by_gen(GA1_cor_grid_6_file, "Grid 6: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[5])

boxplot_cors_by_gen(GA1_cor_grid_7_file, "Grid 7: Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax, mycolor=thecolors[6])

@@

### Plot 1
```{r, GA1 cor by dif windows}
ginmin = 0
ginmax = 5000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

@@

```{r, GA1 cor by dif windows 2}
ginmin = 5000
ginmax = 10000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 3
```{r, GA1 cor by dif windows 3}
ginmin = 10000
ginmax = 15000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 4
```{r, GA1 cor by dif windows 4}
ginmin = 15000
ginmax = 20000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 5
```{r, GA1 cor by dif windows 5}
ginmin = 20000
ginmax = 25000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 6
```{r, GA1 cor by dif windows 6}
ginmin = 25000
ginmax = 30000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 7
```{r, GA1 cor by dif windows 7}
ginmin = 30000
ginmax = 35000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 8
```{r, GA1 cor by dif windows 8}
ginmin = 35000
ginmax = 40000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 9
```{r, GA1 cor by dif windows 9}
ginmin = 40000
ginmax = 45000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```

### Plot 10
```{r, GA1 cor by dif windows 10}
ginmin = 45000
ginmax = 50000
boxplot_cor_grid_by_gen(all_cor_grid, "Simulation Correlation By Grid Number Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)
```
